---
title: "Week 10 Assignment- extra credit"
author: "Jiaxin Zheng"
date: "2024-12-04"
output:
  pdf_document: default
  html_document: default
---
In Text Mining with R, Chapter 2 looks at Sentiment Analysis.  https://www.tidytextmining.com/sentiment.html
In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document.  You should provide a citation to this base code.  You’re then asked to extend the code in two ways:

Work with a different corpus of your choosing, and
Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).
As usual, please submit links to both an .Rmd file posted in your GitHub repository and to your code on rpubs.com.  You make work on a small team on this assignment.

```{r}
library(tidyr)
library(dplyr)
library(httr)  
library(tidytext)
library(readtext)
library(textdata)
library(stringr)
library(janeaustenr)
library(ggplot2)
library(wordcloud)
library(reshape2)
library(RColorBrewer)
```

```{r}
df<- read.csv("https://raw.githubusercontent.com/Jennyjjxxzz/Data607_Week10Assignment/refs/heads/main/sentimentdataset.csv") %>% 
  select(c(Platform, Text))

tok_df<- df %>% 
  unnest_tokens(word, Text)

data("stop_words")
clean_df<- tok_df %>% 
  anti_join(stop_words)
```

```{r}
print(tok_df)
```

```{r}
word_freq <- tok_df%>%
  count(word, sort = TRUE)

# View word frequency
print(word_freq)
```


```{r}
# Get sentiment lexicon
sentiment_lexicon <- get_sentiments("bing")

sentiment_analysis <- tok_df %>%
  inner_join(sentiment_lexicon, by = "word") %>%
  count(word, sentiment, sort = TRUE)

print(sentiment_analysis)
```

```{r}
wordcloud(words = word_freq$word, freq = word_freq$n, min.freq = 2, 
          max.words = 100, random.order = FALSE, colors = brewer.pal(8, "Dark2"))
```

```{r}
platform_sentiment <- clean_df %>%
  inner_join(sentiment_lexicon, by = "word") %>%
  group_by(Platform, sentiment) %>%
  summarise(count = n(), .groups = "drop")


ggplot(platform_sentiment, aes(x = Platform, y = count, fill = sentiment)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Overall Sentiment by Platform",
       x = "Platform",
       y = "Count of Sentiments") +
  theme_bw()
```

